Transfer Learning in Visual and Relational Reasoning

### 2019-11-23 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
font adjustments

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1cm} \and  
Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
Tomasz Kornuta\thanks{Currently at Nvidia. \textit{Santa Clara, CA, USA}.} \and
\hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
Emre Sevgen\thanks{Currently at Citrine Informatics}  \hspace{1cm} \and 
Ahmet S. Ozcan\footnotemark[1] \and \\
IBM Research AI
}

>>>>

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1.5cm} \and  
Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1.5cm} \and 
Tomasz Kornuta\thanks{Currently at NVIDIA. \textit{Santa Clara, CA, USA}.}  \and
\hspace{1cm} Vincent Albouy\footnotemark[1]  \hspace{1.5cm} \and 
Emre Sevgen\thanks{Currently at Citrine Informatics.}  \hspace{1.5cm} \and 
Ahmet S. Ozcan\footnotemark[1] \and \\
{\large IBM Research AI}
}
